### 2019-05-24 2-Chapters/Conclusion/conclusion.tex
SHIT I'm going home

\begin{itemize}
    \item
The first half, Part~\ref{part:Introduction}, starts by motivating our work and situating the context of this research.
% Chapter 2
In Chapter~\ref{chapter:2}, we present the multi-armed bandit models, the hypotheses we usually make, and the most important algorithms used to solve MAB problems.
% Chapter 3
Then in Chapter~\ref{chapter:3} we discuss in details about our open-source Python library developed to run numerical simulations of MAB problems, SMPyBandits.

    \item
The second half of this thesis, Part~\ref{part:MABIOT}, presents our main contributions.
% Chapter 4
In Chapter~\ref{chapter:4}, we first propose some models for realistic IoT wireless networks, in discrete times and with no central coordination between end-devices.
% In two different models, with or without retransmissions, we showed that end-devices can learn independently to increase their successful transmission rates in the network, by using low-cost MAB algorithm. We also present a proof-of-concept that implements such network on real radio hardware and validates our model and proposed algorithms.
% Chapter 5
Because the models studied for realistic IoT networks were found to be intractable to analyze from a theoretical point of view, mainly due to the large number of algorithms interacting at random times in a noisy environment,
in Chapter~\ref{chapter:5}, we study a weaker but still very interesting model.
We present different variants of the multi-player MAB model, and we propose the state-of-the-art algorithm for the variant with collision information (\MCTopM-\klUCB).
% Chapter 6
Finally, in Chapter~\ref{chapter:6}, we remove the stationary hypothesis on the single-player MAB problem, and we analyze a new actively adaptive algorithm (\GLRklUCB).
%
For the last two chapters, our proposed algorithms attain state-of-the-art performances both on numerical simulations and on the regret bounds obtained in our theoretical analyses.
\end{itemize}

>>>>

% \begin{itemize}
%     \item
The first half, Part~\ref{part:Introduction}, starts by motivating our work and situating the context of this research.
% Chapter 2
In Chapter~\ref{chapter:2}, we present the multi-armed bandit models, the hypotheses we usually make, and the most important algorithms used to solve MAB problems.
% Chapter 3
Then in Chapter~\ref{chapter:3} we discuss in details about our open-source Python library developed to run numerical simulations of MAB problems, SMPyBandits.

    % \item
The second half of this thesis, Part~\ref{part:MABIOT}, presents our main contributions.
% Chapter 4
In Chapter~\ref{chapter:4}, we first propose some models for realistic IoT wireless networks, in discrete times and with no central coordination between end-devices.
% In two different models, with or without retransmissions, we showed that end-devices can learn independently to increase their successful transmission rates in the network, by using low-cost MAB algorithm. We also present a proof-of-concept that implements such network on real radio hardware and validates our model and proposed algorithms.
% Chapter 5
Because the models studied for realistic IoT networks were found to be intractable to analyze from a theoretical point of view, mainly due to the large number of algorithms interacting at random times in a noisy environment,
in Chapter~\ref{chapter:5}, we study a weaker but still very interesting model.
We present different variants of the multi-player MAB model, and we propose the state-of-the-art algorithm for the variant with collision information (\MCTopM-\klUCB).
% Chapter 6
Finally, in Chapter~\ref{chapter:6}, we remove the stationary hypothesis on the single-player MAB problem, and we analyze a new actively adaptive algorithm (\GLRklUCB).
%
For the last two chapters, our proposed algorithms attain state-of-the-art performances both on numerical simulations and on the regret bounds obtained in our theoretical analyses.
% \end{itemize}
